\stktokens{}: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-10-21 fully-abstract-comp/popl2019/paper.tex
comment inserted

Regions in $\Regionh$ specify the presence of an invariant in the system, shared with the rest of the system.
\begin{align*}
  \Regionh &= 
             \left\{\begin{multlined}
               \{\pure \} \times (\Wor \monnefun \URel{\MemSeg}) \times \\
               (\Seal \parfun \Wor \monnefun \URel{\SealableCaps \times \SealableCaps})
             \end{multlined}\right.\\
  \Regions &={}
             \left\{\begin{multlined}
               \{\spatial,\spatialo \} \times (\Wor \monnefun \URel{\MemSeg^2}) \cup{} \{\revoked\}
             \end{multlined}\right.
\end{align*}
Shared regions are tagged with the syntactic token $\pure$ and may prescribe two different types of requirements.
First, they may require the presence of \srccm{} and \trgcm{} memory segments
satisfying a given relation in $\Wor \monnefun \URel{\MemSeg^2}$
% Lau: Where do you return to this? I did not find it very clear what it meant when I was done reading about the worlds.
(see below for the meaning of $\Wor \monnefun$).
A region might, for example, require the presence of a certain list of instructions at a given set of memory addresses in both \srccm{} and \trgcm{}.
If a memory segment is owned by a given region, then that memory segment must be disjoint from the memory segments owned by all other regions.
Second, a shared region may also contain a partial function from seals to relations on pairs of sealable capabilities: $\Seal \parfun \Wor \monnefun \URel{\SealableCaps \times \SealableCaps}$.
When the region defines such a relation for a given seal, then no other region in the world can do the same, and any value signed with that seal will be required to satisfy the registered relation.

>>>>

Regions in $\Regionh$ specify the presence of an invariant in the system, shared with the rest of the system.
\begin{align*}
  \Regionh &= 
             \left\{\begin{multlined}
               \{\pure \} \times (\Wor \monnefun \URel{\MemSeg}) \times \\
               (\Seal \parfun \Wor \monnefun \URel{\SealableCaps \times \SealableCaps})
             \end{multlined}\right.\\
  \Regions &={}
             \left\{\begin{multlined}
               \{\spatial,\spatialo \} \times (\Wor \monnefun \URel{\MemSeg^2}) \cup{} \{\revoked\}
             \end{multlined}\right.
\end{align*}
Shared regions are tagged with the syntactic token $\pure$ and may prescribe two different types of requirements.
First, they may require the presence of \srccm{} and \trgcm{} memory segments
satisfying a given relation in $\Wor \monnefun \URel{\MemSeg^2}$
% Lau: Where do you return to this? I did not find it very clear what it meant when I was done reading about the worlds.
(see below for the meaning of $\Wor \monnefun$).
\todo[inline]{LB: I don't think it was explained below}
A region might, for example, require the presence of a certain list of instructions at a given set of memory addresses in both \srccm{} and \trgcm{}.
If a memory segment is owned by a given region, then that memory segment must be disjoint from the memory segments owned by all other regions.
Second, a shared region may also contain a partial function from seals to relations on pairs of sealable capabilities: $\Seal \parfun \Wor \monnefun \URel{\SealableCaps \times \SealableCaps}$.
When the region defines such a relation for a given seal, then no other region in the world can do the same, and any value signed with that seal will be required to satisfy the registered relation.
